Make a Map for our Paper

### 2024-07-02 001-map-of-samples.Rmd
Clean up Snakemake stuff in 001

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_knit$set(root.dir = here::here())
start_time <- Sys.time()

USING_SNAKEMAKE <- FALSE
NEG_USING_SMK <- TRUE
if(exists("snakemake")) {
  USING_SNAKEMAKE <- TRUE
  NEG_USING_SMK <- FALSE
}
```

```{r rmd_snakemake_hacks, include=FALSE, eval=USING_SNAKEMAKE}
# currently, this block does not get evaluated, while developing,
# but later when we snakemake-ize it all, we will evaluate it.
if(USING_SNAKEMAKE) {
  input_list <- snakemake@input
  output_list <- snakemake@output
}
```

@@

```{r}
# inputs:
input_list <- list(
  oregon_rivers = "inputs/Rivers_OR/Rivers_OR.shp"
)
# outputs:
output_list <- list(
  map = "results/map_of_samples/map.pdf",
  cropmap = "results/map_of_samples/map-crop.pdf",
  texmap = "tex/images/map-crop.pdf"
)
# you can create the necessary output directories like this:
dump <- lapply(output_list, function(x)
  dir.create(dirname(x), recursive = TRUE, showWarnings = FALSE)
)
```

@@

Now look add stuff to that:

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_knit$set(root.dir = here::here())
start_time <- Sys.time()
```

@@

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  # inputs:
  input_list <- list(
    oregon_rivers = "inputs/Rivers_OR/Rivers_OR.shp"
  )
  # outputs:
  output_list <- list(
    map = "results/map_of_samples/map.pdf",
    cropmap = "results/map_of_samples/map-crop.pdf",
    texmap = "tex/images/map-crop.pdf"
  )
}

# we create the necessary output directories like this:
dump <- lapply(output_list, function(x)
  dir.create(dirname(x), recursive = TRUE, showWarnings = FALSE)
)
```

@@

Now add stuff to that:
